Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline

### 2017-09-17 draft/ms_resub.tex
The version for resubmission

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan
% Version 4; Edits from Alexie
% Version 5; Edits from Alexie; Comments by Jim
% Version 6; Edits from SH; responses to the referee report

%% ------------------------------------------------------------------------------------ %%
\documentclass[useamsfonts]{pasj01}
\twocolumn

@@

\def\redm{\texttt{redMaPPer}}
\def\hscpipe{\texttt{hscPipe}}
\def\synpipe{\texttt{SynPipe}}
\def\cmodel{\texttt{CModel}}
\def\psf{\texttt{PSF}}
\def\forced{\texttt{forced}}
\def\coadd{\texttt{coadd}}
\def\unforced{\texttt{unforced}}
\def\tract{\texttt{tract}}
\def\visit{\texttt{visit}}
\def\tracts{\texttt{tracts}}
\def\visits{\texttt{visits}}
\def\galsim{\texttt{G}{\scriptsize \texttt{AL}}\texttt{S}{\scriptsize \texttt{IM}}}
\def\hst{{\textit{HST}}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}

@@

    \song{
    Throughout this work, all magnitudes are in AB system (\citealt{Oke1974}). 
    Signal--to--noise ratio (\s2n{}) is defined as the ratio between a flux measurement 
    using certain algorithm (e.g. PSF, \cmodel{}) and its corresponding flux uncertainty 
    from \hscpipe{} ($\mathrm{Flux}/\sigma(\mathrm{Flux})$).  
    At the same time, a $5\sigma$ detection is equivalent to a flux measurement with 
    \s2n{}$=5$ using certain algorithm.  
    Such definitions are adopted in other works using HSC SSP data 
    (e.g. \citealt{Bosch2017, HSCDR1}).
    } 
    The code for \synpipe{}, along with documentation and examples, is made available
    on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.

@@

    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed for the Large Synoptic Survey Telescope’s Data Management system
    (\citealt{Ivezic2008, Axelrod2010, Juric2015}) and is described in 
    Bosch\etal (2017). 
    \song{To enhance the flexibility and extensibility of the pipeline, \hscpipe{} 
    is written using a combination of C++ and Python. 
    All computationally intensive pixel-level operations are performed in C++, 
    high-level algorithm and user interface is written in Python.}
    DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. 
    Because\synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{}, we briefly introduce the main steps below along with a 
    few key HSC/LSST terms.

@@

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain various types of 
            photometric measurements (see \citealt{HSCDR1} for details). 
            Here, we focus on characterizing the the \forced{} \texttt{psf} and 
            \cmodel{} photometry. 
            \song{
            Both the \psf{} and \cmodel{} photometry algorithms take the PSF convolution 
            effect into account, and hence can provide consistent \forced{} photometry 
            across all bands and maximizes \s2n{}.  
            Although their accuracies depend on the accuracy of the PSF model and 
            the applicability of the adopted models, they still provide the most useful 
            flux information for stars and galaxies, especially for objects with 
            low-\s2n{}. 
            Please see Section~4 and Appendix~2 of \citet{Bosch2017} for detailed 
            descriptions of these algorithms.  
            }

@@

                \item \song{
                    Details of the HSC \psf{} photometry can be found in 
                    Section~4.9.5 of \citet{Bosch2017}. 
                    In short, 
                    }
                    \hscpipe{} uses matched-filter method to derive PSF magnitude 
                    with the centroid fixed. 
                    The algorithm matches the image of a star with the PSF model 
                    multiplied by an amplitude. 
                    This amplitude parameter is estimated via the inner product of 
                    the image and PSF model after shifting the model to the centroid 
                    of the star, then divide by the effective area of the PSF model.
                    \song{
                    It considers the per-pixel variance information when estimating 
                    the flux error. 
                    Flux uncertainty due to the uncertainty of centroid is ignored 
                    since it is subdominant even when \s2n{} is low. 
                    }

                \item \song{
                    Details about the HSC \cmodel{} photometry can be found in 
                    Section~4.9.9 and Appendix~2 of \citet{Bosch2017}. 
                    }
                    It is based on the version for the SDSS \cmodel{} magnitude 
                    (\citealt{Lupton2001, Abazajian2004}). 
                    \song{
                    It fits an object using both elliptical model with an exponential 
                    profile and de~Vaucouleurs profile with free amplitudes and shapes. 
                    Then it fits a linear combination of both models to the image while 
                    only allowing the amplitude of each component to change.  
                    The last step provides the \cmodel{} flux and flux error used in 
                    this work. 
                    This \cmodel{} flux can be roughly seen as the linear interpolation 
                    between exponential and de~Vaucouleurs models. 
                    Although these models are often not the most appropriate models for 
                    real galaxies, this method is shown to be robust and efficient, 
                    especially for poorly--resolved and/or low \s2n{} galaxies. 
                    }
                    Star--galaxy classification now is also performed based on the 
                    difference between \texttt{psf} and \cmodel{}{} magnitudes.

@@

        \item \song{\synpipe{} works as a special user interface to \hscpipe{}. 
            It will keep developing along with the \hscpipe{} (and \texttt{LSSTpipe}
            in the future). 
            Since both \hscpipe{} and \galsim{} use Python as high-level language, 
            we also choose to use Python for \synpipe{} to make the frequent 
            interactions among them easy and straightforward. 
            Most of the computationally expensive tasks are handled by the low-level 
            algorithms in \hscpipe{} and \galsim{} in C++, the usage of Python will not 
            affect the overall efficiency of \synpipe{}.
            }

@@

        \item \textbf{\ser{}models}:
            \texttt{SynPipe} uses \galsim{} \texttt{v1.4} (\citealt{Rowe2015}) to
            simulate galaxies.
            \galsim{} is an image simulation tool that was designed for the 
            GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge
            (\citealt{Mandelbaum2014}). 
            Currently, \synpipe{} allows synthetic galaxies to be modeled by a
            single or a double \citet{Sersic1963}
            profile\footnote{More flexible model choices will be added later.}. 
            The \ser{} profile is flexible enough to describe the overall flux
            distributions of galaxies near and far, both early-type or late-type.
            A double-\ser{} model can simulate a galaxy with even more realistic
            structural details (e.g., bulge$+$disk).
            For each \ser{} component, the user needs to provide the magnitude,
            effective radius ($R_{\mathrm{e}}$, in unit of arcsec), \ser{} index
            ($n_{\mathrm{Ser}}$), axis ratio ($\mathrm{b}/\mathrm{a}$), and position
            angle (PA).
            External shear can also be applied to a synthetic galaxy ($g_1$ and
            $g_2$, see \citealt{Rowe2015} for more details).
            \song{ 
            To correctly generate synthetic image of \ser{} or double-\ser{} galaxy
            model, it is not trivial to carefully consider details in pixel 
            integration (especially for central pixel) and image rendering process.  
            Details about these can be found in Section 5 and Section 6 of 
            \citet{Rowe2015}.
            }

@@

            \item \song{For galaxy using any parametric model, we generate 
                rectangular cutout image too. 
                The model image can be truncated at $N \times R_{\rm e}$ to reduce the 
                size of the cutout and speed up the injection process. 
                In this work, we truncate all \ser{} model at $10 \times R_{\rm e}$. 
                The results presented here are not sensitive to this choice.}

@@

    Using the infrastructure provided by \hscpipe{}, the user can easily perform these 
    steps in parallel.  
    \song{
    For \texttt{coadd} images that include the same number of single-\texttt{Visit} 
    data, the overall efficiency of \synpipe{} is similar to the real data reduction
    process under the same computational conditions (e.g. same number of cores). 
    The \texttt{stack.py} and \texttt{multiBand.py} steps should cost very similar 
    amount of time. 
    The single-\texttt{Visit} process is replaced with the injection of synthetic 
    objects. 
    The speed of this step depends on the total number of fake objects injected and 
    the type of the synthetic object (e.g. fake galaxy using \ser{} model costs more 
    time than fake star).
    For tests with reasonable density of fake objects per CCD (e.g. the tests in this 
    work), the injection step costs slightly less time than the actual 
    single-\texttt{Visit} data processing. 
    }
    The data and catalog volumes is also similar to the original data reduction process.

@@

    We use a synthetic star sample built using data from the HST/ACS catalog of 
    \citet{Leauthaud2007}.  
    We first select stars from the \citet{Leauthaud2007} catalog (this classification 
    is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag). 
    We then match this sample against our HSC UltraDeep--COSMOS data (which reaches 
    ${\sim}27.2$ mag in $i$ band). 
    After applying basic quality cuts (see \ref{app:qc}), this procedure provides us 
    with five-band HSC PSF photometry for 14,472 stars.
    To increase the sample size, we re-sample the five-band magnitude distributions 
    using the \texttt{astroML} (\citealt{astroml}) implementation of the 
    \texttt{extreme-deconvolution} algorithm developed by \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
    generate 100,000 synthetic stars. 
    Fig \ref{fig:star_sample} shows the magnitude and color distributions of real 
    COSMOS stars compared to the resampled distributions in all five-bands and in 
    color-color space.
    \song{
    It is worth noting that \synpipe{} test using synthetic stars can also help 
    determine the detection limit and point sources completeness of the HSC data. 
    However, both of them depend on seeing or background conditions, and show 
    spatial variations that need to be considered.  
    It normally requires higher density of synthetic objects to carefully test this 
    and is beyond the scope of this work.  
    Please see Section~5.6 and Section~5.7 of \citet{HSCDR1} for investigation of 
    this topic for HSC SSP DR1 using different method.
    }

    For synthetic galaxies, we use single-\ser{} galaxy models of COSMOS galaxies with 
    $I_{F814W} \leq 25.2$ mag. 
    These are models from \citet{Lackner2012} applied to \textit{HST}/ACS images and 
    are included in \galsim{}. 
    Each model is described by a total of five parameters: magnitude, effective radius,
    \ser{} index, axis ratio, and position angle.
    \song{
    It is worth noting that although single-\ser{} profile is still oversimplified model 
    compared to the complexity in real galaxies, they are flexible enough to broadly 
    describe the flux distributions of most galaxies, and test the \cmodel{} algorithm 
    who models galaxy in very different way.
    In addition, single-\ser{} model is simple enough to ensure straightforward 
    diagnostic of potential systematic issues of \cmodel{} algorithm. 
    }
    We exclude a tiny fraction (${\sim}4$\%) of ill-behaved models that have a very 
    high \ser{} index ($n_{\mathrm{Ser}} > 6.0$) or a very low central surface 
    brightness ($\mu_{i} < 24.0$\sb).
    We further match this COSMOS sample with the HSC UltraDeep--COSMOS data.
    After removing objects with problematic photometry (see Appendix \ref{app:qc} for 
    details), we obtain a sample of 58,210 synthetic galaxies with realistic 
    five-band HSC \cmodel{} photometry.
    As shown in Fig \ref{fig:galaxy_sample}, the majority of these galaxies are
    faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec).
    This sample is appropriate to test \hscpipe{}'s general photometric behaviors, 
    but the sample lacks relatively bright galaxies ($i<20.5$ mag).

@@

    The \s2n{} for PSF photometry is defined as
    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
    \song{
    The flux error here is estimated based on the per-pixel variance information that
    summaries statistical uncertainties from various sources. 
    However, systematical one like the centroid uncertainty is not taken into account 
    as it should be subdominant even at low-\s2n{}. 
    As mentioned earlier, such definition of PSF \s2n{} is adopted by \citet{HSCDR1} 
    and \citet{Bosch2017}.
    }
    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
    in the $g$- and $i$-bands. 
    This figure shows the expected \s2n{} of stars as a function of magnitude in the 
    Wide layer.
    The slopes and scatters of these relations are very similar to the ones using 
    real stars on these two \tracts{}.

@@

    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
    average seeing conditions.
    However, it is worth reminding HSC data users that the detection
    limit will exhibit spatial variations due to the seeing conditions.
    \song{
    In addition, the image warping process introduces covariance across pixels into 
    \texttt{coadd} images, and leads to slightly underestimated the flux error.  
    Therefore, it is useful to compare the statistical results from our tests with the 
    average PSF flux error at fixed input magnitude.  
    }
%% ------------------------------------------------------------------------------------ %%

@@

    The precision of PSF magnitude for the \texttt{badSeeing} \tract{} shows similar 
    performance at $i_{\mathrm{Input}}<23.5$ mag. 
    At fainter magnitudes, the precision slightly degrades. 
    The \texttt{badSeeing} \tract{} has ${\sim}4$\% precision at
    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% precision at
    $i_{\mathrm{Input}}{\sim}25.0$ mag.
    \citet{HSCDR1} evaluates the precision of PSF magnitude via external comparisons
    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds it at 1-2\% level,
    which is consistent with our results. 
    However, at fainter magnitudes, external comparisons become difficult due to the 
    lack of imaging matched to HSC depths.
    The results from \synpipe{} hence provide useful evaluations of the precision of 
    the HSC photometry down to our detection limit\footnote{Strictly speaking, the 
    precision reported here should be considered as upper limits because 
    \synpipe{} currently does not consider the systematic uncertainties in PSF 
    modeling. But this effect should be subdominant.}
    \song{
    On Fig~\ref{fig:psf_mag}, we also compare the \synpipe{} test results with the 
    median \psf{} magnitude error obtained by \hscpipe{} in each bin after taking 
    the aperture correction (see Section~4.9.2 in \citealt{Bosch2017}) uncertainty 
    into account (pairs of grey long-dashed lines on each plot). 
    We find that, for \psf{} photometry, the flux errors from \hscpipe{} are very 
    close to what we estimate using \synpipe{} once the aperture correction 
    error is considered.
    Without the aperture correction error, it seems that \hscpipe{} underestimate 
    the statistical uncertainties of \psf{} magnitude, most likely due to the 
    correlated noises introduced during the image warping and stacking step.
    }

@@

    Fig \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
    color distributions of the input sample to the recovered color distributions. 
    Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors accurately recover the distributions of all four colors 
    and the color-color distributions.
    \song{
    On the $(i-z)$-$(z-y)$ color plane, stars with extreme colors are not well 
    recovered.  
    Fraction of these stars is very low, and it could relate to the scattered 
    light in $y$-band that is still unaccounted for (see Section~5.8.14 of 
    \citealt{HSCDR1}). 
    }

    As for highly blended stars, Fig \ref{fig:psf_color} also shows that highly blended 
    stars have worse precision and accuracy in their colors compared to isolated stars. 
    At fixed input magnitude, the precision in $(g-i)$ is ${\sim}0.1$ mag worse for 
    highly blended stars.  
    \song{
    Unlike \psf{} magnitudes, where the distributions of magnitude differences 
    for highly--blended stars are clearly off, the distributions of \psf{} color 
    differences do peaks around zero.  
    Although the long asymmetric tails still indicate severe biases of \psf{} colors 
    for blended stars: $(g-i)$ color is clearly biased towards bluer colors, while 
    $(i-y)$ color shows bias towards redder values.
    The performances of \psf{} magnitude and color are still poor for highly-blended 
    stars in the current version of \hscpipe{}.  
    Object deblending becomes much more challenging at the depth of HSC SSP, and 
    the current deblending algorithm is known to have problems 
    (see Section~4.8 of \citealt{Bosch2017}) that could cause the problem here. 
    The deblending algorithm is also being constantly updated now, and we will keep 
    using \synpipe{} to evaluate its performance. 
    }

	The statistical uncertainties of \forced{} PSF colors are summarized in 
	Table \ref{tab:psfcolor}. 
	\song{
	On Fig~\ref{fig:psf_color}, we also compare the \synpipe{} results with the 
	uncertainties of \psf{} color obtained by \hscpipe{} (pair of grey long-dashed 
	lines). 
	Here, we simply add the magnitude errors from both bands in quadrature. 
	We find that the average uncertainties of \psf{} color from \hscpipe{} are 
	consistent with the results of \synpipe{} test. 
	Although we should emphasize again that the uncertainties of PSF models are not 
	taken into account. 
    }

@@

    Fig \ref{fig:cmodel_sn} shows the relation between the input magnitudes and the 
    \s2n{} of synthetic galaxies.  
    The \s2n{} is the ratio  of the \cmodel{} flux and the flux error measured by 
    \hscpipe{}.
    \song{
    For extended object with all kinds of flux distributions, definition of \s2n{} is 
    not as straightforward as for point sources.  
    Here the adopted \s2n{} corresponds to the average \s2n{} over entire footprint. 
    The center of the galaxy typically has high \s2n{} than this value.    
    We adopt this definition as the main purpose here is to demonstrate the overall 
    ``significancy'' of galaxy down to certain magnitude. 
    }

>>>>

% Version 0; Rough outline by SH
% Version 1; First draft by SH
% Version 2; Finish main text; with edits from Susan Foster
% Version 3; More edits from Susan
% Version 4; Edits from Alexie
% Version 5; Edits from Alexie; Comments by Jim
% Version 6; Edits from SH; responses to the referee report
% Version 7; Edits from Rachel Mandelbaum, Alexie Leauthaud
% Version: For resubmission

%% ------------------------------------------------------------------------------------ %%
%\documentclass[useamsfonts]{pasj01}
\documentclass[proof]{pasj01}
%\twocolumn

@@

\def\redm{\texttt{redMaPPer}}
\def\hscpipe{\texttt{hscPipe}}
\def\synpipe{\texttt{SynPipe}}
\def\cmodel{\texttt{CModel}}
\def\forced{\texttt{forced}}
\def\coadd{\texttt{coadd}}
\def\psf{\texttt{PSF}}
\def\unforced{\texttt{unforced}}
\def\tract{\texttt{tract}}
\def\visit{\texttt{visit}}
\def\tracts{\texttt{tracts}}
\def\visits{\texttt{visits}}
\def\galsim{\texttt{G}{\scriptsize \texttt{AL}}\texttt{S}{\scriptsize \texttt{IM}}}
\def\hst{{\textit{HST}}}
\def\s2n{{$\mathrm{S}/\mathrm{N}$}}

@@

    \song{
    Throughout this work, all magnitudes are in the AB system (\citealt{Oke1974}). 
    Signal--to--noise ratio (\s2n{}) is defined as the ratio between a flux measurement 
    using a specific algorithm (e.g. PSF, \cmodel{}) and its corresponding flux uncertainty 
    from \hscpipe{} ($\mathrm{Flux}/\sigma(\mathrm{Flux})$).  
    A $5\sigma$ detection is equivalent to a flux measurement with 
    \s2n{}$=5$ using the chosen flux measurement algorithm.  
    The same definitions were adopted in other work using HSC SSP data 
    (e.g. \citealt{Bosch2017, HSCDR1}).
    } 
    The code for \synpipe{}, along with documentation and examples, is made available
    on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.

@@

    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed for the Large Synoptic Survey Telescope’s Data Management system
    (\citealt{Ivezic2008, Axelrod2010, Juric2015}) and is described in 
    Bosch\etal (2017). 
    \song{To enhance the flexibility and modularity of the pipeline, \hscpipe{} 
    is written using a combination of C++ and Python. 
    All computationally intensive pixel-level operations are performed in C++, 
    while high-level connections between routines and the user interface are written in Python.}
    DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. 
    Because\synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{}, we briefly introduce the main steps below along with a 
    few key HSC/LSST terms.

@@

        \item \textbf{HSC Photometry}:
            The multi-band catalogs generated by \hscpipe{} contain various types of 
            photometric measurements (see \citealt{HSCDR1} for details). 
            Here, we focus on characterizing the the \forced{} \texttt{psf} and 
            \cmodel{} photometry. 
            \song{
            Both the \psf{} and \cmodel{} photometry algorithms take the PSF convolution 
            effect into account, and hence can provide consistent \forced{} photometry 
            across all bands and maximize \s2n{}.  
            Although their accuracy depends on the accuracy of the PSF model and choice of a model, they still provide the most useful 
            flux information for stars and galaxies, especially for objects with 
            low-\s2n{}. 
            Please see Section~4 and Appendix~2 of \citet{Bosch2017} for detailed 
            descriptions of these algorithms.  
            }

@@

                \item \song{
                    Details of the HSC \psf{} photometry can be found in 
                    Section~4.9.5 of \citet{Bosch2017}. 
                    In short, 
                    }
                    \hscpipe{} uses matched-filter method to derive PSF magnitude 
                    with the centroid fixed. 
                    The algorithm matches the image of a star with the PSF model 
                    multiplied by an amplitude. 
                    This amplitude parameter is estimated via the inner product of 
                    the image and PSF model after shifting the model to the centroid 
                    of the star, then divide by the effective area of the PSF model.
                    \song{
                    It considers the per-pixel variance information when estimating 
                    the flux error. 
                    Flux uncertainty due to the uncertainty of centroid is ignored 
                    since it is subdominant even when the \s2n{} is low. 
                    }

                \item \song{
                    Details about the HSC \cmodel{} photometry can be found in 
                    Section~4.9.9 and Appendix~2 of \citet{Bosch2017}. 
                    }
                    It is based on the algorithm used for the SDSS \cmodel{} magnitude 
                    (\citealt{Lupton2001, Abazajian2004}). 
                    \song{
                    It fits an object using elliptical models with an exponential 
                    profile and de~Vaucouleurs profile with free amplitudes and shapes. 
                    Then it fits a linear combination of both models to the image while 
                    only allowing the amplitude of each component to change.  
                    The last step provides the \cmodel{} flux and flux error used in 
                    this work. 
                    This \cmodel{} flux can be roughly seen as the linear interpolation 
                    between exponential and de~Vaucouleurs models. 
                    Although these models are often not the most appropriate models for 
                    real galaxies, this method is shown to be robust and efficient, 
                    especially for poorly--resolved and/or low \s2n{} galaxies. 
                    }
                    Star--galaxy classification now is also performed based on the 
                    difference between \texttt{psf} and \cmodel{}{} magnitudes.

@@

        \item \song{\synpipe{} works as a special user interface to \hscpipe{}. 
            It will keep developing along with the \hscpipe{} (and \texttt{LSSTpipe}
            in the future). 
            Since both \hscpipe{} and \galsim{} use Python as their high-level language, 
            we also choose to use Python for \synpipe{} to make the frequent 
            interactions among them easy and straightforward. 
            Most of the computationally expensive tasks are handled by low-level 
            algorithms in \hscpipe{} and \galsim{} that are written in C++.  As a result, the fact that high-level routines are written in Python does not 
            affect the overall efficiency of \synpipe{}.
            }

@@

        \item \textbf{\ser{}models}:
            \texttt{SynPipe} uses \galsim{} \texttt{v1.4} (\citealt{Rowe2015}) to
            simulate galaxies.
            \galsim{} is an image simulation tool that was designed for the 
            GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge
            (\citealt{Mandelbaum2014}). 
            Currently, \synpipe{} allows synthetic galaxies to be modeled by a
            single or a double \citet{Sersic1963}
            profile\footnote{More flexible model choices will be added later.}. 
            The \ser{} profile is flexible enough to describe the overall flux
            distributions of galaxies near and far, both early-type or late-type.
            A double-\ser{} model can simulate a galaxy with even more realistic
            structural details (e.g., bulge$+$disk).
            For each \ser{} component, the user needs to provide the magnitude,
            effective radius ($R_{\mathrm{e}}$, in unit of arcsec), \ser{} index
            ($n_{\mathrm{Ser}}$), axis ratio ($\mathrm{b}/\mathrm{a}$), and position
            angle (PA).
            External shear can also be applied to a synthetic galaxy ($g_1$ and
            $g_2$, see \citealt{Rowe2015} for more details).
            \song{ 
            To generate a synthetic image of a \ser{} or double-\ser{} galaxy
            model with a high level of numerical accuracy, the pixel integration (especially for central pixel) and image rendering process must be carefully handled.  
            Details about these can be found in Section 5 and Section 6 of 
            \citet{Rowe2015}, with validation of numerical accuracy also shown in that paper.
            }

@@

            \item \song{For galaxies using any parametric model, we also generate 
                rectangular cutout images. 
                The model image can be truncated at $N \times R_{\rm e}$ to reduce the 
                size of the cutout and speed up the injection process. 
                In this work, we truncate all \ser{} models at $10 \times R_{\rm e}$. 
                The results presented here are not sensitive to this choice.}

@@

    Using the infrastructure provided by \hscpipe{}, the user can easily perform these 
    steps in parallel.  
    \song{
    For \texttt{coadd} images that include the same number of single-\texttt{Visit} 
    data, the overall efficiency of \synpipe{} is similar to the real data reduction
    process under the same computational conditions (e.g., same number of cores). 
    The \texttt{stack.py} and \texttt{multiBand.py} steps take similar 
    amounts of time. 
    The single-\texttt{Visit} process is replaced with the injection of synthetic 
    objects. 
    The speed of this step depends on the total number of fake objects injected and 
    the type of the synthetic object (e.g., a fake galaxy using a \ser{} model costs more 
    time than a fake star).
    For tests with a reasonable density of fake objects per CCD (e.g., the tests in this 
    work), the injection step takes slightly less time than the actual 
    single-\texttt{Visit} data processing. 
    }
    The data and catalog volumes is also similar to the original data reduction process.

@@

    We use a synthetic star sample built using data from the HST/ACS catalog of 
    \citet{Leauthaud2007}.  
    We first select stars from the \citet{Leauthaud2007} catalog (this classification 
    is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag). 
    We then match this sample against our HSC UltraDeep--COSMOS data (which reaches 
    ${\sim}27.2$ mag in $i$ band). 
    After applying basic quality cuts (see \ref{app:qc}), this procedure provides us 
    with five-band HSC PSF photometry for 14,472 stars.
    To increase the sample size, we re-sample the five-band magnitude distributions 
    using the \texttt{astroML} (\citealt{astroml}) implementation of the 
    \texttt{extreme-deconvolution} algorithm developed by \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
    generate 100,000 synthetic stars. 
    Fig \ref{fig:star_sample} shows the magnitude and color distributions of real 
    COSMOS stars compared to the resampled distributions in all five-bands and in 
    color-color space.
    \song{
    It is worth noting that \synpipe{} test using synthetic stars can also help 
    determine the detection limit and point source completeness of the HSC data. 
    However, both of those quantities depend on the seeing and background conditions, so their  
    spatial variations must be considered.  
    Doing so requires a higher density of synthetic objects than was used here, and is beyond the scope of this work.  
    Please see Section~5.6 and Section~5.7 of \citet{HSCDR1} for investigation of 
    this topic for HSC SSP DR1 using a different method.
    }

    For synthetic galaxies, we use single-\ser{} galaxy models of COSMOS galaxies with 
    $I_{F814W} \leq 25.2$ mag. 
    These are models from \citet{Lackner2012} applied to \textit{HST}/ACS images and 
    are included in \galsim{}. 
    Each model is described by a total of five parameters: magnitude, effective radius,
    \ser{} index, axis ratio, and position angle.
    \song{
    It is worth noting that although the single-\ser{} profile is still an oversimplified model 
    compared to the complexity in real galaxies, it is flexible enough to broadly 
    describe the flux distributions of most galaxies, and test the \cmodel{} algorithm -- which models the galaxy profile in a different way.
    In addition, the single-\ser{} model is sufficiently simple to serve as a  straightforward 
    diagnostic of potential systematic issues of the \cmodel{} algorithm. 
    }
    We exclude a tiny fraction (${\sim}4$\%) of ill-behaved models that have a very 
    high \ser{} index ($n_{\mathrm{Ser}} > 6.0$) or a very low central surface 
    brightness ($\mu_{i} < 24.0$\sb).
    We further match this COSMOS sample with the HSC UltraDeep--COSMOS data.
    After removing objects with problematic photometry (see Appendix \ref{app:qc} for 
    details), we obtain a sample of 58,210 synthetic galaxies with realistic 
    five-band HSC \cmodel{} photometry.
    As shown in Fig \ref{fig:galaxy_sample}, the majority of these galaxies are
    faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec).
    This sample is appropriate to test \hscpipe{}'s general photometric behaviors, 
    but the sample lacks relatively bright galaxies ($i<20.5$ mag).

@@

    The \s2n{} for PSF photometry is defined as
    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
    \song{
    The flux error here is estimated based on the per-pixel variance information that
    summarizes statistical uncertainties from various sources. 
    However, the flux uncertainty due to the centroid uncertainty is not taken into account, 
    as it should be subdominant even at low-\s2n{}. 
    As mentioned earlier, this definition of PSF \s2n{} is adopted by \citet{HSCDR1} 
    and \citet{Bosch2017}.
    }
    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
    in the $g$- and $i$-bands. 
    This figure shows the expected \s2n{} of stars as a function of magnitude in the 
    Wide layer.
    The slopes and scatters of these relations are very similar to the ones using 
    real stars on these two \tracts{}.

@@

    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
    average seeing conditions.
    However, it is worth reminding HSC data users that the detection
    limit will exhibit spatial variations due to the seeing conditions.
    \song{
    In addition, the image warping process introduces covariance between pixels into 
    \texttt{coadd} images, and leads to slightly underestimated flux errors.  
    Therefore, it is useful to compare the statistical results from our tests with the 
    average PSF flux error at fixed input magnitude.  
    }
%% ------------------------------------------------------------------------------------ %%

@@

    The precision of PSF magnitude for the \texttt{badSeeing} \tract{} shows similar 
    performance at $i_{\mathrm{Input}}<23.5$ mag. 
    At fainter magnitudes, the precision slightly degrades. 
    The \texttt{badSeeing} \tract{} has ${\sim}4$\% precision at
    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% precision at
    $i_{\mathrm{Input}}{\sim}25.0$ mag.
    \citet{HSCDR1} evaluates the precision of PSF magnitude via external comparisons
    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds it at 1-2\% level,
    which is consistent with our results. 
    However, at fainter magnitudes, external comparisons become difficult due to the 
    lack of imaging matched to HSC depths.
    The results from \synpipe{} hence provide useful evaluations of the precision of 
    the HSC photometry down to our detection limit\footnote{Strictly speaking, the 
    precision reported here should be considered as upper limits because 
    \synpipe{} currently does not consider the systematic uncertainties in PSF 
    modeling. But this effect should be subdominant.}
    \song{
    On Fig~\ref{fig:psf_mag}, we also compare the \synpipe{} test results with the 
    median \psf{} magnitude error obtained by \hscpipe{} in each bin after taking into account 
    the uncertainty in the aperture correction (see Section~4.9.2 in \citealt{Bosch2017}) -- see the pairs of grey long-dashed lines on each plot. 
    We find that, for \psf{} photometry, the flux errors from \hscpipe{} are very 
    close to what we estimate using \synpipe{} once the aperture correction 
    error is considered.
    Without the aperture correction error, it seems that \hscpipe{} underestimates
    the statistical uncertainties of \psf{} magnitudes, most likely due to the 
    correlated noise introduced during the image warping and stacking step.
    }

@@

    Fig \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
    color distributions of the input sample to the recovered color distributions. 
    Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors accurately recover the distributions of all four colors 
    and the color-color distributions.
    \song{
    On the $(i-z)$-$(z-y)$ color plane, stars with extreme colors are not well 
    recovered.  
    The fraction of these stars is very low, and their poor recovery could relate to the scattered 
    light in $y$-band that is still unaccounted for (see Section~5.8.14 of 
    \citealt{HSCDR1}). 
    }

    As for highly blended stars, Fig \ref{fig:psf_color} also shows that highly blended 
    stars have worse precision and accuracy in their colors compared to isolated stars. 
    At fixed input magnitude, the precision in $(g-i)$ is ${\sim}0.1$ mag worse for 
    highly blended stars.  
    \song{
    Unlike \psf{} magnitudes, where the distributions of magnitude differences 
    for highly--blended stars are clearly biased, the distributions of \psf{} color 
    differences do peak around zero.  
    However, the long asymmetric tails still indicate severe biases of \psf{} colors 
    for blended stars: the $(g-i)$ color is clearly biased towards bluer colors, while the 
    $(i-y)$ color shows a bias towards redder values.
    The performance of \psf{} magnitudes and colors are still poor for highly-blended 
    stars in the current version of \hscpipe{}.  
    Object deblending becomes much more challenging at the depth of the HSC SSP, and 
    the current deblending algorithm is known to have limitations 
    (see Section~4.8 of \citealt{Bosch2017}) that could cause the problem shown here. 
    The deblending algorithm is also being constantly updated now, and we will keep 
    using \synpipe{} to evaluate its performance. 
    }

	The statistical uncertainties of \forced{} PSF colors are summarized in 
	Table \ref{tab:psfcolor}. 
	\song{
	On Fig~\ref{fig:psf_color}, we also compare the \synpipe{} results with the 
	uncertainties of the \psf{} color obtained by \hscpipe{} (pair of grey long-dashed 
	lines). 
	Here, we simply add the magnitude errors from both bands in quadrature. 
	We find that the average uncertainties of \psf{} color from \hscpipe{} are 
	consistent with the results of the \synpipe{} test. 
	Again, we emphasize that the uncertainties of the PSF models are not 
	taken into account. 
    }

@@

    Fig \ref{fig:cmodel_sn} shows the relation between the input magnitudes and the 
    \s2n{} of synthetic galaxies.  
    The \s2n{} is the ratio  of the \cmodel{} flux and the flux error measured by 
    \hscpipe{}.
    \song{
    For extended object with a wide variety of light profiles, the definition of \s2n{} is 
    not as straightforward as for point sources.  
    Here the adopted \s2n{} corresponds to the average \s2n{} over the entire footprint. 
    The center of the galaxy typically has higher \s2n{} than this value.    
    We adopt this definition, as the main purpose here is to demonstrate the overall 
    ``significance'' of the galaxy detections down to a certain magnitude. 
    }
